A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add limitations intro
Add integer multiplication part to Limitations

>>>>

Some limitation were already mentioned briefly. This section provides a deeper
insight on what cannot be accomplished using the standard OBDD representation.
This includes classes of Boolean function which cannot be computed efficiently
using OBDDs and, again, the variable ordering problem.

Already in 1986, Bryant~\cite{BRYANT86} noticed that some classes of Boolean
functions cannot be represented by an OBDD efficiently, regardless of the variable
ordering chosen. He then studied the complexity of Boolean functions in
1991~\cite{BRYANT91} to provide a lower bound on the OBDD as data structure (and
very large scale integrated circuits). The complexity was expressed in the minimum
size of the OBDD, i.e. the minimal number of nodes for any possible variable
ordering $\pi$. Bryant~\cite{BRYANT91} mainly focused on the set of integer
multipliers having word size $n$.

Bryant~\cite{BRYANT91} first generalized a function over $2n$ variables. The size
of an OBDD then can range from $2n$ up to $2^{n+1}-2$ for different variable
orderings. Now, analyzing $n$-bit integer multiplication, Bryant~\cite{BRYANT86}
already proved that for any variable ordering, there exists an $0 \le i \le 2n$
such that the function representing output $i$ requires an OBDD of size
$\Omega(1.09^n)$. Bryant himself~\cite{BRYANT91} showed that there is not much
of a difference between computing the single output $(n-1)$ or the entire product
of an $n$-bit integer multiplier. Bryant~\cite{BRYANT91} found the $n$-bit integer
multiplication to be especially hard, requiring an OBDD having at least $2^{n/8}$
nodes to compute the middle bit of the built product for any variable ordering.
Hence, the complexity of an OBDD representing integer multiplication is
exponential in $n$, where $n$ denotes the word size of the multiplied integers.

\tbr
